Learning Useful Changes\\(to Reduce Runtimes and Software Defects)

### 2015-08-22 Manuscript.tex
Updates from ShareLaTeX

\documentclass{sig-alternate}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{cite}
\usepackage[shortlabels]{enumitem} 
\usepackage{amsmath}
\usepackage{url}
\usepackage{balance}
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\setlist{nolistsep,leftmargin=5mm}
%\usepackage[pdftex]{graphicx}
\usepackage{program}
\newcommand{\Sample}{{\bf SAMPLE}}
\newcommand{\PEEKING}{{\bf PEEKING2}}
%\usepackage[table]{xcolor}
\definecolor{darkgreen}{rgb}{0,0.3,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{url}
\usepackage{hyperref}
\usepackage{listings}
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\title{Learning Useful Changes\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{3} 
\author{
\alignauthor 
Rahul~Krishna,~Tim Menzies,~Xipeng~Shen \\
       \affaddr{Com. Sci., NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Naveen   Lekkalapudi\\
 \affaddr{Software Consultant } \\ 
       \affaddr{Washington D.C.}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 As business users demand more insightful
 analytics, data scientists need to change
 their tools. Instead of merely predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  how to change values in order to
 improve on some predicted value.

This paper is aims to study such planners. The planners fall into three broad categories (1) Cluster specific planners (K Nearest Neighbors); (2) Instance specific planners (HOW); (3) Decision Tree based planners. These planners are employed as tools for proposing changes to independent
 variables in order to improve on 
 the predictions of the dependent variables. Unlike other approaches
 for learning optimizations to software, these planners do not require
 an underlying model of the domain. Also, these plans
 are designed to result in {\em minimal displacement}
 to current practice.

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 45\%,61.5\%  (median) and 22\%,6\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. For  case 
studies, we apply CROSSTREES to   (1)~reduce the predicted number
of defects and (2)~reduce the runtimes of five system.

@@

Our approach is important for two reasons. Firstly, business users now demanding analytics tools that support a business-level interpretation of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in data mining and software engineering~\cite{menzies12a}. Panelists commented that ``prediction is all well and good, but what about decision making?''. That is, these panelists are more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. For example:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
A second reason for the importance of our approach is, as shown below,
when asked how to change a project in order to achieve a result, it is surprisingly
difficult to use standard methods (e.g. clustering) to find those changes.
In the case study that motivated this paper, we how  standard data mining methods
can generate  seemingly
useful insights, but which are in fact completely ineffectual. On the other hand,
using CROSSTREES, we can propose changes that significantly reduce:
\bi
\item The  defects found  in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item The runtime of the  software    configured by  Seigmund et al.~\cite{sven12}.
\ei 
Since CROSSTREES is a somewhat novel algorithm, we present it in tutorial form.
The next section walks the reader through a sequence of approaches that start
with a standard clustering algorithm, and progresses on to CROSSTREES. The second
half of the paper then presents an extensive evaluation of CROSSTREES on 
the Jureczko  and Seigmund data sets. This is followed by notes on related work
and validity.

\section{ Methods for Learning Changes}
 This paper experimentally compares four methods for inputting software project data and outputting
 recommendations on what to change.
 For case studies that illustrate how this method works, we use data from Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10} (shown in \fig{ck} and \fig{jd}) and
  software system   configuration data from by  Seigmund et al.~\cite{sven12} (see \fig{cpm}).

  The Jurecko data records number of known defects for each class, where the classes are described in terms of
  nearly two dozen metrics such as number of children, lines of code, etc.

  The Seigmund data records the runtime of compiled systems. To generate that data, Seigmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). To ensure that the perturbations
  were valid, the option space was modeled as a tree that included knowledge of what
  options were mandatory, optional, or were alternatives (see \fig{bdbc}).
  Given those perturbations, the systems were then compiled and 
  Seigmund et al. recorded how long each perturbation took to complete a test suite.

@@

 \begin{figure}
 \scriptsize
 \begin{center}
 \begin{tabular}{r|rr}
 data set & cases & \% defective\\\hline
  ant &947& 22\\
  camel& 1819& 19\\
 jedit& 1257& 2\\
 ivy &352& 11\\
 log4j& 244 &92\\
 lucebe &442 &59\\
 poi& 936 &64\\
 synapse &379 &34\\
 velocity& 410& 34\\
 xalan& 2411& 99\\
 xerces &1055& 74
 \end{tabular}
 \end{center}
 \caption{The Jureczko data sets (columns in the format of \fig{ck}).}\label{fig:jd}
 \end{figure}

@@

\caption{Seigmund data sets: details on the data sets.
For SQLite, the data  contains 4,553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}\label{fig:cpm}
\end{figure}

\begin{figure}[!t]
\includegraphics[width=1\linewidth]{_figs/BDBC.eps}
\caption{Feature model for the Berkeley database (``C'' version). }\label{fig:bdbc}
\end{figure}

Research has shown that given the above data, it is possible to build
predictors for defective classes (in the Jureczko data) or for the runtime
of a compiled system (in the Seigmund data) (e.g. see ~\cite{sven12,nam13,he13,peters13,Menzies2013:local,me09b,me11f,me07b}).
This paper is about the next step {\em after} prediction. We envisonage as scenario
where business users are presented a prediction and they do not like what they see; e.g. the runtimes are too long of the number of defects is too high. Such users will
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?'' The rest of this paper
defines and explores four methods for generating those plans.

\subsection{Method1: Centroid Deltas}

In the summer of 2011 and 2012, one of us (Menzies) spent two months
	working on-site at Microsoft Redmond,
	observing data mining analysts.  In that study, he took special
	note about how Microsoft's data scientists
	discussed the results of their data mining sessions with  business users.

@@

Turning now to the Seigmund data, the lessons learnt from the planners advise on how  to change the configurations settings within a Makefile (in order to make resulting compiled code  run faster). Here, performance can be measured in terms of  difference between the predicted runtime $p$ of test case items and their actual runtimes $a$ using  $s=\frac{abs(a - p)}{a}$.

This paper  explores six Seigmund configuration data sets:  Berkeley DB (Java and C versions), Apache, SQLite, LLVM, and
  x264\footnote{Available from the performance prediction section of PROMISE
  http://openscience.us/repo/performance-predict.}. 
  After splitting that data into equal sized train:test groups, a Random Forest
  Regressor trained on one half, then applied to the other, achieved nearly perfect scores of \[s=\{99.9, 99.8, 99.4, 99.1, 96.1\}\]

That is, we can be very confident that the predictors from the Seigmund data can assess
our plans. (Aside: if the reader doubts that such high scores are achievable, we note that these scores are consistent with those achieved by predictors built by Seigmund et al.~\cite{sven12}.)

@@

\subsection{Assessment}
\fig{work} showed how we build and test our planners. The dependent variables of Jureczko and Seigmund data sets are discrete and continuous in nature, respectively. Hence, while choosing the predictor, we used Random Forest (1) as a classifier for Jureczko data and (2) as a regressor for Seigmund data. Additionally, for both the data sets, we designed a setup that repeated the trials 40 times (the value 40 was chosen to satisfy the minimum sample size requirements of the central limit theorem):
\bi
\item For Seigmund data, we randomized the order of the data, training on one half while identifying treatment plans on the remaining test data.
\item For the Jureczko data, we used the training and testing sets of \fig{j}. 
\ei
The 40 repeats defined above were repeated for each planner. A Scott-Knott procedure was used to test for statistical differences in the result. The Scott-Knott procedure was recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{mittas13}.

@@

\subsection{Results}
\input{tex/deltas_avg.tex}
The results for each data, for different planners, are shown in \fig{jur} and \fig{conf}. All
\subsection{Discussion}
\section{Threats to Validity}
\input{tex/results_models.tex}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}

>>>>

\documentclass{sig-alternate}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{cite}
\usepackage[shortlabels]{enumitem} 
\usepackage{amsmath}
\usepackage{url}
\usepackage{balance}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
%\setlist{nolistsep,leftmargin=5mm}
%\usepackage[pdftex]{graphicx}
\usepackage{program}
\newcommand{\Sample}{{\bf SAMPLE}}
\newcommand{\PEEKING}{{\bf PEEKING2}}
%\usepackage[table]{xcolor}
\definecolor{darkgreen}{rgb}{0,0.3,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{url}
\usepackage{hyperref}
\usepackage{listings}
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\title{Learning Useful Changes\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{3} 
\author{
\alignauthor 
Rahul~Krishna\\Tim Menzies, Xipeng~Shen \\
       \affaddr{Com. Sci., NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Naveen   Lekkalapudi\\
 \affaddr{Bellhops } \\ 
       \affaddr{Washington D.C.}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 As business users demand more insightful
 analytics, data scientists need to change
 their tools. Instead of just predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  what to change  in order to
 improve on the predicted values.

This paper is aims to study such planners. The planners fall into three broad categories (1) Cluster-specific planners (K Nearest Neighbors); (2) Instance specific planners (HOW); (3) Decision Tree based planners. 
Our experiments show that the latter (decision tree planners)
works best, measured both in terms of the {\em simplicity} of the plan
and the {\em size} of the improvements.
For example, in the   test data of this paper, the  improvements   reduce
 the expected values of defect counts and  runtimes to    
 45\%,61.5\%  (median) and 22\%,6\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. For  case 
studies, we apply CROSSTREES to   (1)~reduce the predicted number
of defects and (2)~reduce the runtimes of five system.

@@

Our approach is important for two reasons. Firstly, business users now demanding analytics tools that support a business-level interpretation of their data. At a panel on software analytics at ICSE`12, industrial practitioners lamented the state of the art in data mining and software engineering~\cite{menzies12a}. Panelists commented that ``prediction is all well and good, but what about decision making?''. That is, these panelists are more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. For example:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
A second reason for the importance of our approach is, as shown below,
when asked how to change a project in order to achieve a result, it is surprisingly
difficult to use standard methods (e.g. clustering) to find those changes.
In the case study that motivated this paper, we how  standard data mining methods
can generate  seemingly
useful insights, but which are in fact completely ineffectual. On the other hand,
using CROSSTREES, we can propose changes that significantly reduce:
\bi
\item The  defects found  in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item The runtime of the  software    configured by  Siegmund et al.~\cite{sven12}.
\ei 
Since CROSSTREES is a somewhat novel algorithm, we present it in tutorial form.
After describing our test data,
this paper  walks the reader through a sequence of approaches that start
with a standard clustering algorithm, and progresses on to CROSSTREES. The second
half of the paper then presents an extensive evaluation of CROSSTREES on 
the Jureczko  and Siegmund data sets. This is followed by notes on related work
and validity.

@@

\section{Test Domains}
 This paper experimentally compares four methods for inputting software project data and outputting
 recommendations on what to change. For case studies that illustrate how this method works, we use data from Jureczko et al.'s object-oriented JAVA systems~\cite{jureczko10}  and
  software system   configuration data from by  Siegmund et al.~\cite{sven12}.

   The Jurecko data records number of known defects for each class, where the classes are described in terms of
  nearly two dozen metrics such as number of children, lines of code, etc.
For details on the Jurecko data, see  \fig{ck} and \fig{jd}.

  The Siegmund data records  runtimes of compiled systems. To make that data, Siegmund et al. perturbed
  the configuration parameters in the Makefiles of six systems: Apache, SQLite, LLVM, x264 and two versions of the
  Berkeley database (one written in ``C'' and one in Java). 
  Given those perturbations, the systems were then compiled and 
  Siegmund et al. recorded how long each perturbation took to run a test suite. For details on the Siegmund  data, see \fig{cpm}.
  To ensure that the perturbations
  were valid, the option space was modeled as a tree that included knowledge of what
  options were mandatory, optional, or were alternatives (see \fig{bdbc}).

 \begin{figure}
 \scriptsize
 \begin{center}
 \begin{tabular}{r|rr}
 data set & cases & \% defective\\\hline
  ant &947& 22\\
  camel& 1819& 19\\
 jedit& 1257& 2\\
 ivy &352& 11\\
 log4j& 244 &92\\
 lucebe &442 &59\\
 poi& 936 &64\\
 synapse &379 &34\\
 velocity& 410& 34\\
 xalan& 2411& 99\\
 xerces &1055& 74
 \end{tabular}
 \end{center}
 \caption{ Jureczko data: columns in the format of \fig{ck}.}\label{fig:jd}
 \end{figure}

@@

\caption{Siegmund data.
For SQLite, the data  contains 4,553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}\label{fig:cpm}
\end{figure}

\begin{figure}[!t]
\includegraphics[width=1\linewidth]{_figs/BDBC.eps}
\caption{ Berkeley database feature model   (``C'' version). }\label{fig:bdbc}
\end{figure}

\section{Methods for Learning Changes}
Research has shown that given the above data, it is possible to build
predictors for defective classes (in the Jureczko data) or for the runtime
of a compiled system (in the Siegmund data); e.g. see ~\cite{sven12,nam13,he13,Menzies2013:local,me09b,me11f,me07b}.

This paper is about the next step {\em after} prediction. Suppose
a business user is presented a prediction and they do not like what they see; e.g. the runtimes are too long of the number of defects is too high. This user may
then ask a {\em planning}  question; i.e. ``what can we change to do better than that?'' The rest of this paper
defines and evaluates different methods for answering that question.

\subsection{Method0: Non-automatic Approaches}

For the purposes of completeness, we offer first some notes
on how  {\em not} to generate recommendations for changes.

One way to change projects for the better is to ask smart experienced
people for their opinion on how to (e.g.) reduce defects and/or decrease runtimes. Sometimes
such advice 
is an effective strategy and sometimes it is not.
According to Passos et al.~\cite{passos11},  warn that developers
may  assume that the lessons they learn from a few past
projects are general to 
all their future projects. They comment ``past experiences were taken into account without 
much consideration for their context~\cite{passos11}.  
 J{\o}rgensen \& Gruschke~\cite{jorgensen09} concur with Passos et al. They report that 
  supposed software engineering    ``gurus'' rarely use lessons
  from past projects to improve their future reasoning and that such poor
  past advice can be detrimental to new projects.~\cite{jorgensen09}.
  Based on that research, we proposed a ``trust, but verify'' approach.
  If a software guru offers some sage wisdom, then it is wise to (a)~follow that
  advice but (b)~also ask some other oracle if there were any better options
  (just as a sanity check).
  The rest of this paper discusses some methods to build automatic oracles 
  to implement that   sanity check.

Another way find good changes to a project
would be to rely
on the peer review processes used by the 
SE research community. This approach would propose changes to software
projects that concur with internationally accept best practices. There are three
problems with that approach. Firstly, given the rapid pace of change in software
engineering, we may be asking questions for which there is no currently accept
``best practice''. For example, only very recently has there been any work
of predicting software runtimes based on choices within Makefiles. While the work
of Siegmund et al.~\cite{sven12} is certainly state of the art, it does
cannot yet represent ``internationally accept best practices'' since that work is so
recent.

Secondly, given the diversity of SE products and practices
and personnel, it may well be that the current project being discussed is 
substantively different to prior work. 
Numerous recent {\em local learning} results compare (1) single models
learned from all available data to (2) multiple models learned from clusters within the data~\cite{betten14,yang11,yang13,minku13,me12d,me11m,posnett11}.
A repeated result in those studies in that the local models generated the better effort
and defect predictions (better median results,
lower variance in the predictions).

In summary, 
it is useful to have automatic methods to recommend changes. Such
methods can fill in for human gurus (if such gurus are absent) or 
offer a second opinion that (possibly)  a different perspective to the human guru.
Also, prior to making automatic recommendations, it is wise to first stratify the data
(clump it into related examples) then generate advice specific to each clump.
In the following, we will use various methods that generate numerous clumps as follows:
  $N$ examples will be divided into groups containing at most $\alpha=\sqrt{N}$
  examples\footnote{We denote variables
  set via  engineering judgement  with Greek letters; e.g. $\alpha$.
  In this paper, we show our current settings to these variables produces useful
  results.  Future papers should check if different
  settings to these variables are more useful.}.

 This clumping to gether of different examples  can be operationalized in numerous ways. Consider  a table of data
with many independent features and one dependent feature (where the latter is usually called
the ``class''):
\bi
\item
Method1, Method2, and Method3
use ``unsupervised clustering''; i.e. examples are clumped together if they have
similar values for their independent features. 
\item
Method4 uses ``supervised clustering'';
i.e. examples are clumped together if that  reduces the dependent feature {\em variability}.
\ei
For or continuous and discrete values,
the {\em variability} can be measured using standard deviation\footnote{$\sigma = \sqrt{\sum^n_i \left( (x_i - \bar{x})^2/(n-1)\right)}$} or entropy\footnote{If $n$ discrete values occur at frequency
$f_1,f_2,.. f_n$, then \mbox{$N = \sum n_i$} and $p_i = f_i/N$ and entropy is 
$-1 * \sum_i p_ilog_2(p_i)$.}, respectively).  
\subsection{Method1: Sorted Centroids}

One method for learning changes is as follows.  
  Cluster project data by reflecting just on the indepedent variables,
  Next, build one centroid for each cluster (using the median and mode value for continuous
and discrete values, respectively).
After that, write a spreadsheet with one column per centroid;
\bi
\item
Sort the columns such that any current projects client fall into the left-most
columns. That is, make the left-hand-side of the sheet  ``current usual practice''
and the right-hand side  ``alternatives to current usual practice''.
\item
Sort the rows of that spreadsheet such that the rows with
maximum  variability appear at the top 
\ei
Now show the sheet to the business user, encouraging them to make recommendations by
\bi
\item
Comparing the left and right-sided columns;
\item
Using the features mentioned in the top-most rows (where changes selects for the most different centroids).
\ei
	Recent results suggest that, we clustering on independent variables of software project data,
	we are free to select from a wide range of 
	clustering methods.  Ganesan~\cite{div14} explored 
	different clustering methods for SE data using   effort and defect data from
	the PROMISE repository~\cite{promiserepo}.
	That study explored
	K-Means, mini-batch-K-Means, DBscan, EM, Ward, and the WHERE algorithm discussed
	below.
	Clusters were assessed via the performance of prediction 
	learned from the clusters by Random Forests (for defect prediction)
	and M5prime or linear regression (for effect estimation).  Ganesan found
	that the details of the clustering method were less important than ensuring that  a large number of clusters were generated.

	Accordingly, we select a clustering method that generates a large
	number of small cluster
	($\sqrt{N}$ clusters
	from $N$ examples, that runs fasts, which has shown promise in prior work~\cite{Menzies2013}, and which ignores spurious dimensions (the last item is important since, in our experience, much SE data is ``noisey''; i.e. contains signals not associated with the target variable). For the rest of this article,
	we use  the top-down
	bi-clustering method described in \fig{contast_trees} which recursively divides the
	data in two  using a dimension that captures the greatest variability in the data. 
	\begin{figure}[t]\small
	\begin{tabular}{|p{.95\linewidth}|}\hline 
		WHERE  divides data into  groups of size $\alpha=\sqrt{N}$ using 
		 Aha et al.'s standard Euclidean distance measure~\cite{aha91}.  For $F$ independent features, the measure returns   $d(X,Y)=\sqrt{\sum_i^F \left(\Delta(X_i,Y_i)^2\right)}/\sqrt{F}$
			(the denominator normalizes the output to $0 \le d \le 1$).
			Within $\Delta$, if   $X_i,Y_i$ are both missing  values, then  return 1.
			Otherwise, replace any  missing items with values that maximizes the following.
			For numerics $\Delta$ normalizes $X_i,Y_i$ (to the range 0,1 for min,max) then
			returns 
			$X_i - Y_i$. For discrete variables, $\Delta$ returns 0,1 if $X_i,Y_i$ are the
			same,different (respectively).  
		Using this measure, WHERE runs as follows:
		\begin{enumerate}[leftmargin=3mm]
			\item Find   two   distance cases,  $X,Y$
			by picking any case $W$ at random, then setting $X$ to its most
			distant case, then setting $Y$ to the case most distant from
			$X$
			(which requires only $O(2N)$ comparisons).
			\item Project each case $Z$
			to position $x$ along a    lines that  runs from $X$ to $Y$, If $a,b$ re distances  $Z$ to $X,Y$  then  $x = (a^2+c^2 - b^2)/(2ac)$.
			\item Split the data at the median $x$ value of all cases.
			\item For   splits larger than  $\sqrt{N}$, call this algorithm recursively  from step1.
		\end{enumerate}\\\hline
		\end{tabular}
		\caption{Top-down division of data with WHERE.}\label{fig:where}
		\end{figure}

In theory, One  advantage of this method is that it focuses the attention of the business users
away from rows that do not select for different centroids and towards differences between
current usual practice and everything else.  
In the summer of 2011 and 2012, one of us (Menzies) spent two months
	working on-site at Microsoft Redmond,
	observing data mining analysts.  In that study, he took special
	note about how Microsoft's data scientists
	discussed the results of their data mining sessions with  business users.

@@

Turning now to the Siegmund data, the lessons learnt from the planners advise on how  to change the configurations settings within a Makefile (in order to make resulting compiled code  run faster). Here, performance can be measured in terms of  difference between the predicted runtime $p$ of test case items and their actual runtimes $a$ using  $s=\frac{abs(a - p)}{a}$.

This paper  explores six Siegmund configuration data sets:  Berkeley DB (Java and C versions), Apache, SQLite, LLVM, and
  x264\footnote{Available from the performance prediction section of PROMISE
  http://openscience.us/repo/performance-predict.}. 
  After splitting that data into equal sized train:test groups, a Random Forest
  Regressor trained on one half, then applied to the other, achieved nearly perfect scores of \[s=\{99.9, 99.8, 99.4, 99.1, 96.1\}\]

That is, we can be very confident that the predictors from the Siegmund data can assess
our plans. (Aside: if the reader doubts that such high scores are achievable, we note that these scores are consistent with those achieved by predictors built by Siegmund et al.~\cite{sven12}.)

@@

\subsection{Assessment}
\fig{work} showed how we build and test our planners. The dependent variables of Jureczko and Siegmund data sets are discrete and continuous in nature, respectively. Hence, while choosing the predictor, we used Random Forest (1) as a classifier for Jureczko data and (2) as a regressor for Siegmund data. Additionally, for both the data sets, we designed a setup that repeated the trials 40 times (the value 40 was chosen to satisfy the minimum sample size requirements of the central limit theorem):
\bi
\item For Siegmund data, we randomized the order of the data, training on one half while identifying treatment plans on the remaining test data.
\item For the Jureczko data, we used the training and testing sets of \fig{j}. 
\ei
The 40 repeats defined above were repeated for each planner. A Scott-Knott procedure was used to test for statistical differences in the result. The Scott-Knott procedure was recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{mittas13}.

@@

\subsection{Results}
\input{tex/deltas_avg.tex}
The results for each data, for different planners, are shown in \fig{jur} and \fig{conf}. All
\subsection{Discussion}
\section{Threats to Validity}
\input{tex/results_models.tex}
\section{Conclusion}

works for more than defects and tunrimes

\section*{Acknowledgements}
The work has partially funded by a National Science Foundation CISE CCF award \#1506586.
\bibliographystyle{plain}
